Check Coverage

### 2019-10-07 analysis/merge_data.Rmd
Revamp how coverage is measured

Are there any studies for which we have trait data for all species?
```{r}
merge_data <- function(taxa, trait_data){
  biotime_data %>%
    select(-sourceName, -scientificName) %>%
  filter(taxa == taxa) %>%
  left_join(trait_data, by = "id",
            na_matches = "never")
}

get_coverage <- function(taxa_data){
  coverage <- taxa_data %>%
  group_by(study_id) %>%
  summarise(perc = sum(!is.na(sourceName))/n()) %>%
  arrange(desc(perc))
}

get_coverage(merge_data("Birds", elton_bird)) %>% View
get_coverage(merge_data("Mammals", elton_mamm)) %>% View()
get_coverage(merge_data("Amphibians", amphibio)) %>% View()
```

@@

traits <- list(elton_bird, elton_mamm, amphibio)
taxa <- list("Birds", "Mammals", "Amphibians")

biotime_traits_list <- map2(taxa, traits, ~merge_data(taxa = .x, trait_data = .y))

#this gives a coverage for each trait dataset, so potentially a lot of coverage with one dataset and no coverage on all the rest
#need to get rid of zeros when there is coverage from another dataset so we only have one entry per study
coverage <- map_dfr(biotime_traits_list, get_coverage) %>% 
  filter(perc > 0)%>%
  right_join(biotime_data %>% select(study_id) %>% distinct()) %>%
  mutate(perc = replace_na(perc, 0))

@@

biotime_traits <- map_dfr(biotime_traits_list, ~drop_na(., scientificName)) %>%
  filter(study_id %in% inc_coverage$study_id)
```

>>>>

Are there any studies for which we have trait data for all species?
```{r}
merge_data <- function(trait_data){
  biotime_data %>%
    select(-sourceName, -scientificName) %>%
  left_join(trait_data, by = "id",
            na_matches = "never") %>%
    drop_na(scientificName)
}
```

@@

traits <- list(elton_bird, elton_mamm, amphibio)

comp_biotime_traits <- map_dfr(traits, merge_data) %>%
  right_join(biotime_data %>% select(-sourceName, -scientificName))

#always check that one species didn't match to multiple datasets, below should return and empty dataframe
#comp_biotime_traits %>% group_by(record_id) %>% filter(n() > 1) %>% dim()

#this gives a coverage for each trait dataset, so potentially a lot of coverage with one dataset and no coverage on all the rest
#need to get rid of zeros when there is coverage from another dataset so we only have one entry per study
coverage <- comp_biotime_traits %>%
  group_by(study_id) %>%
  summarise(perc = sum(!is.na(sourceName))/n()) %>%
  arrange(desc(perc))

@@

biotime_traits <- comp_biotime_traits %>%
  filter(study_id %in% inc_coverage$study_id)
```
